A Partitioning Algorithm for Maximum Common Subgraph Problems

### 2017-08-11 poster/poster.tex
Tweaked poster

@@

\begin{columns}
\column{1}
{
    \colorlet{blockbodybgcolor}{uofgcobalt}
    \colorlet{blocktitlebgcolor}{uofgcobalt}
    \block[bodyverticalshift=0.5cm, bodyinnersep=3mm]{}{
        \centering\begin{minipage}{0.94\textwidth}
            \Large We introduce a new \textbf{branch and bound} algorithm for the \textbf{maximum common
            subgraph} and \textbf{maximum common connected subgraph} problems which is based
            around vertex labelling and partitioning. Our method resembles
            a constraint programming approach, but uses a novel compact
            domain store to reduce
            the memory and computation requirements.  Experiments
            show a \textbf{speedup of more than an order of magnitude} over the state of the
            art, and demonstrate that we can operate on \textbf{much larger graphs} without
            running out of memory.
%            We show how to generate \textbf{really hard} random instances for \textbf{subgraph
%            isomorphism} problems. For the non-induced variant, we predict and observe a phase
%            transition between satisfiable and unsatisfiable instances, with a corresponding
%            complexity peak seen in \textbf{three different solvers}. For the induced variant, much
%            richer behaviour is observed, and \textbf{constrainedness} gives a better measure of
%            difficulty than does proximity to a phase transition. We also discuss \textbf{variable
%            and value ordering} heuristics, and their relationship to the \textbf{expected number of
%            solutions}.
        \end{minipage}
        \vspace*{0.4cm}
    }
}
\end{columns}

@@

\block{The Maximum Common Subgraph Problem}{
\begin{wrapfigure}[7]{r}{0.47\linewidth}
    \begin{flushright}\begin{tikzpicture}[scale=1.6]%{{{
        \node[draw, circle, fill=uofgrose, inner sep=8pt, font=\bfseries] (Na) at (1,  0)
        {\vphantom{0}};
        \node[draw, circle, fill=uofgrose, inner sep=8pt, font=\bfseries] (Nb) at (1, -2)
        {\vphantom{0}};
        \node[draw, circle, fill=uofgrose, inner sep=8pt, font=\bfseries] (Nc) at (1, -4)
        {\vphantom{0}};
        \node[draw, circle, fill=uofgrose, inner sep=8pt, font=\bfseries] (Nd) at (3, -4)
        {\vphantom{0}};
        \node[draw, circle, fill=white, inner sep=8pt, font=\bfseries] (Ne) at (3, -2)
        {\vphantom{0}};

@@

        \node[draw, circle, fill=uofgrose, inner sep=8pt, font=\bfseries] (N1) at (7.5,  0) {\vphantom{0}};
        \node[draw, circle, fill=white, inner sep=8pt, font=\bfseries] (N2) at (9.5,  0) {\vphantom{0}};
        \node[draw, circle, fill=uofgrose, inner sep=8pt, font=\bfseries] (N3) at (7.5, -2) {\vphantom{0}};
        \node[draw, circle, fill=white, inner sep=8pt, font=\bfseries] (N4) at (9.5, -2) {\vphantom{0}};
        \node[draw, circle, fill=uofgrose, inner sep=8pt, font=\bfseries] (N5) at (7.5, -4) {\vphantom{0}};
        \node[draw, circle, fill=uofgrose, inner sep=8pt, font=\bfseries] (N6) at (9.5, -4) {\vphantom{0}};
        \node[draw, circle, fill=white, inner sep=8pt, font=\bfseries] (N7) at (5.5,  0) {\vphantom{0}};
        \node[draw, circle, fill=white, inner sep=8pt, font=\bfseries] (N8) at (5.5, -2) {\vphantom{0}};
        \node[draw, circle, fill=white, inner sep=8pt, font=\bfseries] (N9) at (5.5, -4) {\vphantom{0}};

@@

\block{See the Paper For\ldots}{
    \begin{itemize}
        \item ~ How to extend the algorithm to handle vertex and edge labels
        \item ~ Additional experimental results
    \end{itemize}
}

>>>>

\definecolor{magmamagenta}{rgb}{0.709804,0.211765,0.478431}

@@

\begin{columns}
\column{1}
{
    \colorlet{blockbodybgcolor}{uofgcobalt}
    \colorlet{blocktitlebgcolor}{uofgcobalt}
    \block[bodyverticalshift=0.5cm, bodyinnersep=3mm]{}{
        \centering\begin{minipage}{0.94\textwidth}
            \Large We introduce a new \textbf{branch and bound} algorithm for the \textbf{maximum common
            subgraph} and \textbf{maximum common connected subgraph} problems which is based
            around vertex labelling and partitioning. Our method resembles
            a constraint programming approach, but uses a novel compact
            domain store to reduce
            the memory and computation requirements.  Experiments
            show a \textbf{speedup of more than an order of magnitude} over the state of the
            art, and demonstrate that we can operate on \textbf{much larger graphs} without
            running out of memory.
        \end{minipage}
        \vspace*{0.4cm}
    }
}
\end{columns}

@@

\block{The Maximum Common Subgraph Problem}{
\begin{wrapfigure}[7]{r}{0.47\linewidth}
    \begin{flushright}\begin{tikzpicture}[scale=1.6]%{{{
        \node[draw, circle, fill=magmamagenta, inner sep=8pt, font=\bfseries] (Na) at (1,  0)
        {\vphantom{0}};
        \node[draw, circle, fill=magmamagenta, inner sep=8pt, font=\bfseries] (Nb) at (1, -2)
        {\vphantom{0}};
        \node[draw, circle, fill=magmamagenta, inner sep=8pt, font=\bfseries] (Nc) at (1, -4)
        {\vphantom{0}};
        \node[draw, circle, fill=magmamagenta, inner sep=8pt, font=\bfseries] (Nd) at (3, -4)
        {\vphantom{0}};
        \node[draw, circle, fill=white, inner sep=8pt, font=\bfseries] (Ne) at (3, -2)
        {\vphantom{0}};

@@

        \node[draw, circle, fill=magmamagenta, inner sep=8pt, font=\bfseries] (N1) at (7.5,  0) {\vphantom{0}};
        \node[draw, circle, fill=white, inner sep=8pt, font=\bfseries] (N2) at (9.5,  0) {\vphantom{0}};
        \node[draw, circle, fill=magmamagenta, inner sep=8pt, font=\bfseries] (N3) at (7.5, -2) {\vphantom{0}};
        \node[draw, circle, fill=white, inner sep=8pt, font=\bfseries] (N4) at (9.5, -2) {\vphantom{0}};
        \node[draw, circle, fill=magmamagenta, inner sep=8pt, font=\bfseries] (N5) at (7.5, -4) {\vphantom{0}};
        \node[draw, circle, fill=magmamagenta, inner sep=8pt, font=\bfseries] (N6) at (9.5, -4) {\vphantom{0}};
        \node[draw, circle, fill=white, inner sep=8pt, font=\bfseries] (N7) at (5.5,  0) {\vphantom{0}};
        \node[draw, circle, fill=white, inner sep=8pt, font=\bfseries] (N8) at (5.5, -2) {\vphantom{0}};
        \node[draw, circle, fill=white, inner sep=8pt, font=\bfseries] (N9) at (5.5, -4) {\vphantom{0}};

@@

\block{See the Paper For\ldots}{
    \begin{itemize}
        \item ~ The algorithm in all its magnificent glory
        \item ~ Additional experimental results
    \end{itemize}
}
